Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Revamped description of store-allocating results

The final approximation we make to get to our baseline analysis is
store-allocating results of application sub-expressions. The semantics
of the previous section is where AAM leaves off. However, notice that
the $\kfn{}$ continuation stores a value - this makes the space of
continuations quadratic rather than linear in 0-CFA. A linear space
drops the complexity to cubic.

To achieve this, we instead allocate an address for the value position
when we create the continuation.  This address and the tail address
are both determined by the label of the application point, so the
space becomes linear and the overall complexity drops to cubic. Note
that this is a critical abstraction in languages with n-ary functions,
since otherwise the continuation space becomes ${\mathcal O}(n^n)$!
This amount of distinction between continuations is unnecessary
in practice.

>>>>

The final approximation we make to get to our point of departure is
store-allocating results of application sub-expressions. 
The AAM approach stops at the previous optimization. 
However, the $\kfn{}$ continuation stores a value, and this makes the space of
continuations quadratic rather than linear in the size of the program---even for a monovariant analysis like 0CFA.
Having the space of continuations grow linearly with the size of the program 
will drop the overall complexity to cubic (as expected).

To achieve this linearity for continuation, we allocate an address for the value position
when we create the continuation.  This address and the tail address
are both determined by the label of the application point, so the
space becomes linear and the overall complexity drops to cubic. 
This is a critical abstraction in languages with $n$-ary functions,
since otherwise the continuation space grows super-exponentially.
% In theory, this aggressive distinction between continuations might buy
% additional precision, but in practice, it does not.
